Unifying Gompertzian growth with the communicable disease spreading paradigm

### 2022-04-29 main.tex
use unnormalized values in tables

\begin{table}[H]
\centering
\caption{Estimated values for the SIRD model fitted to various countries' observations normalized by the last observation, $Y_{max}$, as shown in Figure \ref{fig:Gompertz_vs_SIRD_lnln_infty} using notation from \ref{eq:SIRD_D}. Note that due to normalization values will be different from \citet{carletti2020covid}.}
\begin{tabular}{llll}
\toprule
{} &           $\eta\times 10$ &      $\xi$ &            $\kappa\times 10^{2}$ \\
\midrule
Belgium        &    1.0(1) &  2.9(3) &   9.3(1) \\
Portugal       &   0.55(4) &  4.2(4) &   4.5(4) \\
Austria        &    1.3(3) &  2.3(4) &    11(2) \\
Switzerland    &   1.24(1) &  2.4(2) &  11.0(7) \\
Sweden         &    0.5(2) &    3(1) &     3(2) \\
Italy          &   0.43(1) &  5.6(2) &   3.7(1) \\
France         &   0.88(7) &  3.4(3) &   8.1(6) \\
Spain          &  0.525(1) &  6.2(2) &   4.8(1) \\
Germany        &   0.78(8) &  3.0(3) &   6.5(7) \\
Denmark        &   0.50(4) &  5.2(6) &   4.2(4) \\
United Kingdom &   0.54(2) &  4.7(2) &   4.3(2) \\
Netherlands    &   0.51(3) &  5.0(4) &   4.3(3) \\
Turkey         &   0.84(9) &  2.8(3) &   6.9(8) \\
Iran           &  0.322(7) &  7.2(3) &  2.51(9) \\
US             &  0.339(8) &  7.0(3) &   1.8(1) \\
China          &    3.8(9) &  1.2(2) &    26(4) \\
\bottomrule
\end{tabular}

@@

\begin{table}[H]
\centering
\caption{Estimated values for the Gompertz model fitted to various countries' observations normalized by the last observation, $Y_{max}$, as shown in Figure \ref{fig:Gompertz_vs_SIRD_lnln_infty} using notation from \ref{eq:GompertzODE}.}
\begin{tabular}{llll}
\toprule
{} &             $\nu\times 10$ &           $\beta\times 10^{2}$ &        $\tilde{Y}\times 10^{2}$ \\
\midrule
Belgium        &   2.74(1) &   8.1(2) &  3.6(3) \\
Portugal       &  2.242(6) &  6.23(9) &  3.1(1) \\
Austria        &   2.74(1) &   8.1(2) &  3.6(2) \\
Switzerland    &  2.740(7) &   8.1(1) &  3.6(2) \\
Sweden         &   1.73(3) &   4.3(3) &  2.6(4) \\
Italy          &  2.107(6) &  5.88(9) &  3.0(1) \\
France         &  2.752(1) &   8.2(2) &  3.6(2) \\
Spain          &  2.556(8) &   7.5(1) &  3.4(2) \\
Germany        &  2.335(7) &   6.5(1) &  3.2(1) \\
Denmark        &   2.32(1) &   6.6(2) &  3.2(3) \\
United Kingdom &  2.333(6) &  6.54(9) &  3.2(1) \\
Netherlands    &  2.311(7) &   6.5(1) &  3.2(1) \\
Turkey         &  2.306(7) &   6.4(1) &  3.2(1) \\
Iran           &  1.862(7) &  5.04(9) &  2.7(1) \\
US             &  2.014(8) &   5.3(1) &  2.9(1) \\
China          &  3.155(8) &   9.4(2) &  3.6(2) \\
\bottomrule
\end{tabular}

>>>>

\begin{table}[H]
\centering
\caption{Estimated values for the SIRD model fitted to various countries' observations as shown in Figure \ref{fig:Gompertz_vs_SIRD_lnln_infty} using notation from \ref{eq:SIRD_D}. Standard deviation is given in the paranthesis corresponding to the last significant digit of the reported number.}
\begin{tabular}{llll}
\toprule
{} &           $\eta\times 10^{-1}$ &      $\xi \times 10^{4}$ &            $\kappa\times 10^{2}$ \\
\midrule
Belgium        &    94(8) &   3.2(2) &   9.3(7) \\
Portugal       &   6.6(4) &    35(2) &   4.5(3) \\
Austria        &     8(1) &    36(5) &    11(1) \\
Switzerland    &    22(1) &  13.6(7) &  11.0(5) \\
Sweden         &    19(5) &     8(2) &     3(1) \\
Italy          &   137(3) &  1.77(5) &  3.71(1) \\
France         &  240(10) &  1.24(7) &   8.1(4) \\
Spain          &   145(2) &  2.27(5) &  4.75(8) \\
Germany        &    61(4) &   3.9(3) &   6.5(5) \\
Denmark        &   2.7(2) &    96(8) &   4.3(3) \\
United Kingdom &   181(5) &  1.39(5) &   4.3(1) \\
Netherlands    &    29(1) &   8.9(5) &   4.3(2) \\
Turkey         &    34(3) &   6.8(5) &   6.9(6) \\
Iran           &  22.3(4) &  10.4(4) &  2.51(7) \\
US             &   312(5) &  0.76(2) &  1.83(7) \\
China          &  130(30) &   3.5(5) &    26(4) \\
\bottomrule
\end{tabular}

@@

\begin{table}[H]
\centering
\caption{Estimated values for the Gompertz model fitted to various countries' observations, as shown in Figure \ref{fig:Gompertz_vs_SIRD_lnln_infty} using notation from \ref{eq:GompertzODE}.}
\begin{tabular}{llll}
\toprule
{} &             $\nu\times 10$ &           $\beta\times 10^{2}$ &        $\tilde{Y}\times 10^{2}$ \\
\midrule
Belgium        &   9.3(1) &   8.1(2) &  10.1(9) \\
Portugal       &  6.15(3) &  6.22(7) &   7.0(3) \\
Austria        &  7.28(7) &   8.1(2) &   8.1(7) \\
Switzerland    &  8.08(6) &   8.1(1) &   8.9(5) \\
Sweden         &   4.9(1) &   4.3(2) &     6(1) \\
Italy          &  7.60(6) &  5.88(7) &   8.4(4) \\
France         &  10.2(1) &   8.2(1) &  11.0(8) \\
Spain          &  9.41(9) &   7.5(1) &  10.2(7) \\
Germany        &  7.56(6) &  6.53(8) &   8.4(4) \\
Denmark        &  5.94(7) &   6.5(2) &   6.8(7) \\
United Kingdom &  8.46(5) &  6.54(7) &   9.3(4) \\
Netherlands    &  7.34(6) &  6.52(8) &   8.2(4) \\
Turkey         &  7.04(5) &  6.38(8) &   7.9(4) \\
Iran           &  5.87(6) &  5.04(8) &   6.7(4) \\
US             &  7.53(7) &  5.32(7) &   8.4(5) \\
China          &   9.8(1) &   9.4(2) &    10(1) \\
\bottomrule
\end{tabular}
